Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-15 Paper/paper.tex
Adding a sentence about the PoA being a theoretical lower bound
Have added a sentence justifying why we choose worst case equilibria

The function $f_h$ is well defined as it maximises a continuous function over a finite discrete set (in case of multiple values that minimize $U_h$, it is assumed that $f_h$ returns the lowest such value).

@@

An analysis of the effect of rational behaviour is given for both of these models in the form of PoA calculations.
The PoA is calculated so as to measure the effect of rational behaviour on overall patient throughput.
High PoAs are found in the case of strict diversion which is to be expected as soft diversion implies a certain level of cooperation.
Importantly a non negligible effect of rational behaviour is calculated for certain policy target values.
A recommendation of setting $t=0.72$ is found across both models. This gives some evidence to a particular target value of maximal utilisation in a two CCU ward setting.

>>>>

The function $f_h$ is well defined as it maximises a continuous function over a finite discrete set.
In case of multiple values that minimize $U_h$, it is assumed that $f_h$ returns the lowest such value, this is consistent with the PoA being a theoretical upper bound of the effect of uncoordinated behaviour.

@@

An analysis of the effect of rational behaviour is given for both of these models in the form of PoA calculations.
The PoA is calculated so as to measure the effect of rational behaviour on overall patient throughput.
The PoA represents a theoretical lower bound for the potential damages caused by uncoordinated behaviour.
High PoAs are found in the case of strict diversion which is to be expected as soft diversion implies a certain level of cooperation.
Importantly a non negligible effect of rational behaviour is calculated for certain policy target values.
A recommendation of setting $t=0.72$ is found across both models. This gives some evidence to a particular target value of maximal utilisation in a two CCU ward setting.
